\documentclass{article}

\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{cite}
\usepackage{url}
\usepackage{amsmath}
\usepackage{enumerate}

\begin{document}

\title{Distributed System - Google Deployment}

\author{Andon Tchechmedjiev, 
\and Jander Nascimento}

\maketitle

\section{Prototype}

The \emph{Shortie} is the name of the project for testing and validate the Google Cloud Service.
\emph{Shortie} is a twitter-like application for posting messages, but with no characters limitation. It uses a simple authentication service for Authentication and Autorization.

\section{Specification}

The application will use a couple API's to provide a basic structure for the application development.

\begin{enumerate}
\item Java Servlet API
\item Google APP Engine for Java
\end{enumerate}

\section{Google Cloud service}

Google Clouse service for Java runs on the version 6, but has support for versions 5 and on. The Google Cloud APP automatically provices the Java Servlet API support.
The only requirement is the deployment is the deployment descriptor. 
The JVM runs on a secure sandbox environment assuring that one running application do not interfere in anothers application performance.

\subsection{Account Creation}

For the account creation the requirements are: a google account (gmail for instance) and a telephone number for the Google App engine validation.

After the account creation is possible to check informations like:
\begin{enumerate}
\item CPU Time
\item Bandwidth usage
\end{enumerate}



\subsection{Google Plugin}
\subsection{Debugging}
\subsection{Deployment}
\subsection{Restriction}


\end{document}


